Bootstrap Confidence Intervals for Regression Discontinuity Designs with Uniform Kernels

### 2016-02-22 main_paper.tex
Add fallback when VERSION.tex
Some of the people working on this project (ahem) are not as
excited about the idea of 'automatically generated git commit
information' as others and have resisted generating VERSION.tex.
This commit makes an ugly but seemingly necesary concession to
them and adds a default fallback option if VERSION.tex does not
exist. You're mfing welcome.
Change filepath to BibTeX database
Referring to 'references.bib' causes problems on some TeX
compilers, so we use 'references' instead.
Add Emacs/AucTeX information to main_paper.tex
This commit adds a little bit of configurat

\documentclass[12pt,fleqn]{article}
\input{VERSION}
\input{tex/setup}
\input{tex/macros}

@@

\begin{abstract}
This paper proposes an novel bootstrap procedure to obtain robust bias-corrected
confidence intervals in regression discontinuity designs. The approach proposed 
is based on a first-order bias correction and provides an alternative
to the plug-in analytical methods proposed by Calonico, Cattaneo and Titiunik (2014).
The algorithm is simple to implement and generates robust confidence intervals
with improved coverage relative to the analytical alternatives in simulations.
\end{abstract}

@@

%%%%%REFERENCES%%%%%%%%%
\clearpage
\bibliographystyle{jpe}
\bibliography{tex/references.bib}
\end{document}

>>>>

\documentclass[12pt,fleqn]{article}

% Add commit information from Git to the pdf. It is automatically
% generated with the R script 'R/version.R' and can be run from
% the command line in the project's top directory via:
%
% $ Rscript R/version.R
%
% If VERSION.tex does not exist we can't add information from
% Git, so we'll use today's date as a fallback.

\IfFileExists{./VERSION.tex}{\input{VERSION}}{%
\providecommand\VERSION{\today}}

\input{tex/setup}
\input{tex/macros}

@@

\begin{abstract}\noindent%
  This paper develops a novel bootstrap procedure to obtain robust
  bias-corrected confidence intervals in regression discontinuity designs that
  use the uniform kernel. The procedure uses a residual bootstrap to estimate
  the bias of the RD estimator, which is then removed from the original RD
  estimator. The bias-corrected estimator is then bootstrapped itself to
  generate valid confidence intervals. This procedure is valid for empirically
  relevant bandwidths when the residual bootstraps use a polynomial of higher
  order than used to estimate the treatment effect and can be applied under the
  same conditions as Calonico, Cattaneo and Titiunik's (2014,
  \textit{Econometrica}) analytical correction.
\end{abstract}

@@

\clearpage
\bibliographystyle{jpe}
\bibliography{tex/references}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
